### 2019-06-10 doc/chapters/introduction.tex
fixed
fixed title
Added No Inflation Property.

\section{Formal verification with Stainless}
\label{sec:stainless}

@@

Bitcoin-S is a large project found on GitHub implementing many functionalities.
In this work two of them is going to be examined and worked on, namely the \nameref{property_1} and the \nameref{property_2} describer shortly.
Thus, we go through the relevant code parts to verify those properties, look at some challenges with Stainless and see why we should write software with verification in mind.
We will rewrite the code to Pure Scala, because Bitcoin-S is not written in it.

\subsection{No Inflation Property}
\label{property_1}

>>>>

\section{Formal Verification with Stainless}
\label{sec:stainless}

@@

Bitcoin-S is a large project found on GitHub implementing many functionalities.
In this work we look at two of them, namely the \nameref{property_1} and the \nameref{property_2} described shortly.
Thus, we go through the relevant code parts to verify those properties, look at some challenges with Stainless and see why we should write software with verification in mind.
We will rewrite the code to Pure Scala, because Bitcoin-S is not written in it.

\subsection{No Inflation Property}
\label{property_1}
The decision to verify this property was inspired by the bug found in Bitcoin Core in September 2018  \cite{cve201817144} which could allow to spend the same unspent transaction output (UTXO) in a transaction multiple times.
Hence, new coins could be created out of thin air.
Thus, the property, that a non-coinbase transaction cannot generate new coins, is chosen to be verified in this work.

As we can see later in chapter \ref{chap:verify_check}, we must rewrite the huge fragment of the code implementing this property.
This reimplementation into Pure Scala needs a lot of time.
So, we adjust the plan and verify another functionality of Bitcoin-S.
Nevertheless, during the analysis of the No Inflation Property we have detected and fixed a bug in Bitcoin-S, what is described in section \ref{sec:bugfix}.
